Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-13 article.tex
Added missing redline packages and commands
Modifications by Yoav

%
% Some new commands I use in this text
%
% Note:
% Nice curly font is {\bm{\mathcal{D}}}
%
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\abbrev}[1]{\rm{#1}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
\newcommand{\fix}[2]{\st{#1}\hl{#2}}

@@

\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
  \caption{\small Different viewpoints of a sky that includes {\em
      Haze Blobs}. Images are rendered using the single-scattering model.
    A yellow dot marks the Sun location. Dashed white circles mark
    zenith angles.}
  \label{fig:simulation-results1}
\end{figure}
\Cref{fig:simulation-results1} shows examples of photographs rendered
using the single-scattering model. To create these photographs we
simulated several scenarios, whose details are as follows.
\\

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}. For clarity of display, the brightness of the
displayed pictures in this paper underwent the same standard
contrast enhancement (stretching), including gamma-correction.
The recovery algorithms, of course, uses the raw (not brightness
enhanced) images.

@@

\noindent ({\tt v}) The photon-packet is scattered to a new direction,
determined by inverse transform sampling, according to the phase
function of the particle (Eqs.~\ref{eq:aerosol_scatter}
or~\ref{eq:rayleighP}). This yields a new {\em ray}, denoted ${\cal
  R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
estimation~\cite{marshak20053d} derives the amount of
light back-traced to the sun at each scattering. The next iteration of
propagation (denoted {\tt ii} above) proceeds.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering (dotted) and MC (solid line) forward models.
    (a) cross sections of the {\em Haze Blobs} scene (described in \cref{sec:simul}).
    The difference between the models is much more pronounced (b) 
    when the scatterers are ten times denser (see \cref{sec:optimization-results}).
  }
  \label{fig:cross_sections}
\end{figure}
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small Images simulated by MC, from the same viewpoint, but different
  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function.
  (d) High aerosol density. Details of the scenarios used in creating (b) and
  (c) are given in \cref{sec:optimization-results}.}
  \label{fig:simulation_particles}
\end{figure}

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a).
\Cref{fig:cross_sections} plots the intensity profile
along a horizontal cross section of the viewed field,
comparing photographs simulated using the single-scattering and the  MC forward models.
\Cref{fig:cross_sections}(a) compares photographs \cref{fig:simulation-results1}(d)
and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
This plot demonstrates consistency in this scene, for most pixels.
\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
where the aerosol density was increased ten folds (see \cref{sec:optimization-results}
and the corresponding MC photograph, \cref{fig:simulation_particles}(d)).
In this plot the single-scattering and MC cross sections diverge
due to the effect of the high order scattering.
\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing
to any pixel are accumulated in steps {\tt ii} and {\tt v} above.
The contributing photons that stem from just a single scattering event yield
\cref{fig:scatter_order}(a). Similarly, contributing photons that had
experienced exactly  two or three scattering events yield respectively
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c). First-order
scatter yields most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long
and dense part of the atmosphere, while a vertical LOS cuts short through
the dense, lower part. Hence, toward the horizon the probability of high
order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributions
   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
  \label{fig:scatter_order}
\end{figure}

>>>>

%
% Some new commands I use in this text
%
% Note:
% Nice curly font is {\bm{\mathcal{D}}}
%
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\abbrev}[1]{\rm{#1}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

%
% Red-lined version settings
%
\newcommand{\del}[1]{\sout{#1}}
\newcommand{\rl}[1]{\uwave{#1}}
\newcommand{\fix}[2]{\del{#1}\rl{#2}}
\newcommand{\rleq}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}

@@

\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
  \caption{\small Different viewpoints of a sky that includes {\em
      Haze Blobs}. Images are rendered using the single-scattering model.
    A yellow dot marks the Sun location. Dashed white circles mark
    zenith angles.}
  \label{fig:simulation-results1}
\end{figure}
\Cref{fig:simulation-results1} shows examples of photographs rendered
using the single-scattering model. To create such photographs we
simulated several scenarios, whose details are as follows.
\\

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}. For clarity of display, the brightness of the
displayed pictures in this paper underwent the same standard
contrast enhancement (stretching), including gamma-correction.
The recovery algorithm, of course, uses the raw (not brightness
enhanced) images.

@@

\noindent ({\tt v}) The photon-packet is scattered to a new direction,
determined by inverse transform sampling, according to the phase
function of the particle (Eqs.~\ref{eq:aerosol_scatter}
or~\ref{eq:rayleighP}). This yields a new {\em ray}, denoted ${\cal
  R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
estimation~\cite{marshak20053d} derives the amount of
light back-traced to the sun at each scattering. The next iteration of
propagation (denoted {\tt ii} above) proceeds.

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a).
Similarly, \cref{fig:simulation_particles}(a) corresponds to the same
viewpoint as \cref{fig:simulation-results1}(d).
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small Images simulated by MC, from the same viewpoint, but different
  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function.
  (d) High aerosol density. Details of the scenarios used in creating (b) and
  (c) are given in \cref{sec:optimization-results}.}
  \label{fig:simulation_particles}
\end{figure}
\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing
to any pixel are accumulated in steps {\tt ii} and {\tt v} above.
The contributing photons that stem from just a single scattering event yield
\cref{fig:scatter_order}(a). Similarly, contributing photons that had
experienced exactly  two or three scattering events yield respectively
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c). First-order
scatter yields most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long
and dense part of the atmosphere, while a vertical LOS cuts short through
the dense, lower part. Hence, toward the horizon the probability of high
order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributions
   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
  \label{fig:scatter_order}
\end{figure}

\Cref{fig:cross_sections} plots the intensity profile
along a horizontal cross section of the viewed field,
comparing photographs simulated using the single-scattering and the  MC forward models.
\Cref{fig:cross_sections}(a) is extracted from \cref{fig:simulation-results1}(d)
and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
This plot demonstrates consistency in this scene, for most pixels.
\Cref{fig:cross_sections}(b) plots the same profiles,
where the aerosol density was increased tenfold (see \cref{sec:optimization-results}
and the corresponding MC photograph, \cref{fig:simulation_particles}(d)).
In \cref{fig:cross_sections}(b) the plots differ more than in \cref{fig:cross_sections}(a),
due to high order scattering.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering (dotted) and MC (solid line) forward models.
    (a) cross sections of the {\em Haze Blobs} scene (described in \cref{sec:simul}).
    The difference between the models is much more pronounced (b) 
    when the scatterers are ten times denser (see \cref{sec:optimization-results}).
  }
  \label{fig:cross_sections}
\end{figure}
